\remerciements

First and foremost, I would like to thank the Almighty Allah for granting us the strength to persevere and overcome all difficulties.

\medskip

I would like to express my gratitude to \textbf{\LR{\large{Mr.Abdelghani Ghazdali}}}, the head of the Computer Science and Data Engineering department, who ensured the smooth progress of the supervision sessions from start to finish.

\medskip

I would also like to extend my sincere thanks to \textbf{\LR{\large{Professor Nidal Lamghari}}}, for his valuable advice, expertise, and availability throughout this experience. Your attentive guidance allowed me to deepen my knowledge and improve my technical skills. I am grateful for the opportunity to benefit from your expertise and constant support.

\medskip

At the conclusion of this work, I would also like to express my sincere thanks and gratitude to all those who, through their teaching, support, and advice, contributed to the progress of this project.

\medskip

Furthermore, I would like to express my gratitude to \textbf{\LR{\large{IZICAP}}}, where I had the opportunity to carry out my final year project. I am grateful to the entire \textbf{\LR{\large{IZICAP}}} team for welcoming me warmly and allowing me to apply my academic knowledge in a professional environment. Your expertise, mentorship, and resources have been invaluable in the completion of this project.

\medskip

I would like to give special thanks to \textbf{\LR{\large{Mr.Bilal SLAYKI}}}, my supervisor in the company, for his constant support, wise guidance, and invaluable assistance throughout this project. Your experience, insightful advice, and kindness have inspired me and greatly contributed to my professional growth. I am grateful for sharing your expertise with me and for being an exceptional mentor.

\medskip

Finally, my thanks also go to the entire faculty and administrative staff of ENSA Khouribga for their efforts in providing us with a quality education, as well as the administrative and technical team for all the services provided.