\conclusion

The internship has been a rewarding experience that allowed exploring various aspects of microservices using technologies such as Delta Lake, Trino, Spring Boot, and Keycloak. The work environment was conducive to learning and implementing these concepts.

The adoption of microservices brings numerous advantages over a monolithic architecture. Microservices offer better scalability and flexibility, allowing independent deployment, development, and scaling of each service. Moreover, communication between microservices through APIs facilitates integration and collaboration among different parts of the system.

Throughout the internship, we learned how to design and implement microservices using Spring Boot, leveraging its features for persistence, security, and REST API creation. We also integrated Keycloak to manage user authentication and authorization in our microservices architecture. The use of Delta Lake ensured data reliability and facilitated handling updates.

By successfully transforming the monolithic architecture into a microservices-based architecture, the application achieved improved flexibility, maintainability, performance, data consistency, and modularity. The adoption of React and the microfrontend approach enhanced the frontend development experience and allowed for more modular and independent functionalities.

The internship provided valuable insights into modern application architecture and development practices. It emphasized the importance of considering scalability, flexibility, and modularity when designing and implementing software solutions. The experience gained will undoubtedly contribute to future projects and endeavors in the field of software development.